\chapter{Problem Statement}


{
    With the increase in population and mobile equipments, existing wireless networks 
    have been facing difficulty to withstand increasing traffic load. Thats why,
    5G network is designed in such a way that it will meet these intense demands 
    in addition to security and seamless communication.
    As explained in chapter 2, types of ways to increase the capacity of a network.
    5G network is aimed to use microcells concept. In this a cell is divided into microcells of 
    aprrox. radius of 200m which was 30km in 4G networks. Due to decrease in cell size, 
    high-frequency signals of low penetrability is adopted as 5G networks consist
    of a large number of small Access Points (AP) to provide high data access rates 
    and available network bandwidth. High frequency signal will not interfere with 
    other cells frequency.\\

    But to decrease in the cell size, handover between the Base Station (BS) 
    and mobile equipment become
    very frequent. According to a study, it is said that on an average it will take
    11.6sec to have a handover for a mobile equipment (ME) in 5G network. During handover
    we have use a secure way to authenticate the ME and acess point. And handover
    process should be resistant to any type of attack. But as well as with providing
    security we should also make the it fast to provide the seamless connection to the 
    mobile equipment.\\

    So, we should find a fast and secure way for authentication during the handover.
    
    
}