\chapter*{Reference}

\begin{itemize}
    \item “Is 5G Handover Secure and Private? A Survey” Dongsheng Zhao, Zheng Yan, Senior Member, IEEE, Mingjun Wang, Peng Zhang, and Bin Song, Senior Member, IEEE
    \item Security for 4G and 5G cellular networks: A survey of existing authentication and privacy-preserving schemes Mohamed Amine Ferraga,b,⁎, Leandros Maglarasc, Antonios Argyrioud, Dimitrios Kosmanosd,
    \item A. Talukdar, M. Cudak, and A. Ghosh, “Handoff rates for millimeterwave 5G systems,” in Proc. 79th IEEE Veh. Technol. Conf. (VTC), 2014, pp. 1–5.
    \item A. K. Sutrala, M. S. Obaidat, S. Saha, A. K. Das, M. Alazab, and Y. Park, “Authenticated key agreement scheme with user anonymity and untraceability for 5genabled softwarized industrial cyber-physical systems,” IEEE Transactions on Intelligent Transportation Systems, 2021
    \item R. Canetti and H. Krawczyk, “Universally composable notions of key exchange and secure channels,” in International Conference on the Theory and Applications of Cryptographic Techniques. Springer, 2002, pp. 337–351
    \item https://www.digi.com/blog/post/5g-network-architecture
    \item https://sites.google.com/view/ansuman/wireless-communications-and-networks?authuser=0
    \item https://www.itu.int/en/mediacentre/backgrounders/Pages/5G-fifth-generation-of-mobile-technologies.aspx
    \item C.-C. Chang and H.-D. Le, “A provably secure, efficient, and flexible authentication scheme for ad hoc wireless sensor networks,” IEEE Transactions on wireless communications, vol. 15, no. 1, pp. 357–366, 2015
    \item Burrows, M., Abadi, M., Needham, R.M.: A logic of authentication. Proceedings of the Royal Society of London. A. Mathematical and Physical Sciences 426(1871), 233-271 (1989).
    \item “Desynchronization resistant privacy preserving user authentication protocol for location based services”, PK Roy, A Bhattacharya, Peer-to-Peer Networking and Applications 14 (6), 3619-3633
    \item “A group key-based lightweight Mutual Authentication and Key Agreement (MAKA) protocol for multi-server environment” ,PK Roy, A Bhattacharya, The Journal of Supercomputing, 1-28
    \item “Secure and efficient authentication protocol with user untraceability for global roaming services “, PK Roy, A Bhattacharya, Wireless Networks, 1-18

\end{itemize}